%!TEX root = NSFmaster.tex
%%%%%%%%% BIOGRAPHICAL SKETCH -- 2 pages

\setcounter{section}{0}
\required{Biographical Sketch: Steven Clontz}

% Your Bio should be divided into the following sections
% (a) Professional Preparation (education):
% Undergrad, Major, Year
% Graduate, Major, Year
% Postdoc, Area, Years-Inclusive

\section{Professional Preparation}

\begin{itemize}{}
  \item Auburn University \hspace{3em} Auburn, AL \hspace{3em} Mathematics \hspace{3em} B.S., 2008
  \item Auburn University \hspace{3em} Auburn, AL \hspace{3em} Mathematics \hspace{3em} M.S., 2010
  \item Auburn University \hspace{3em} Auburn, AL \hspace{3em} Mathematics \hspace{3em} Ph.D., 2015
\end{itemize}


% (b) Appointments:  most recent first.

\section{Appointments}

\begin{itemize}
  \item Assistant Professor, The Univerity of South Alabama, 2016-present.
  \item Visiting Assistant Professor, The University of North Carolina at
        Charlotte, 2015-2016.
\end{itemize}

% (c) Publications:  5 related to the proposal, and 5 "Other Significant Publications"

\section{Publications}

\subsection{Related to Proposal}

\begin{itemize}
  \item Clontz, S. and Gruenhage, G.
    \textit{Proximal compact spaces are Corson compact.}
    Topology Appl. 173 (2014), 1-8.
  \item Clontz, S.
    \textit{Zero-Markov information in topological games.}
    Ala. J. Math. 39 (2015).
  \item Clontz, S.
    \textit{Tactic-proximal compact spaces are strong Eberlein compact.}
    Topology Appl. 204 (2016), 306-317.
  \item Clontz, S.
    \textit{On \(k\)-tactics for Gruenhage's compact-point game.}
    Q\&A in Gen. Topology 34 (2016), 1-10.
  \item Clontz, S. and Varagona, S.
    \textit{Destruction of metrizability in generalized inverse limits.}
    Top. Proc. 48 (2016), 289-297.
\end{itemize}

% (d) Synergistic Activities (math-enhancing activities that were not
% part of your main job description, like editorial boards and
% conference organizing - any Math-related volunteer work.
% these are often similar to Broader Impacts

\section{Synergistic Activities}

\begin{itemize}
  \item Director of Mathematical Puzzle Programs, an organization which
        organizes mathematical puzzle events to encourage young people to
        engage in mathematical problem-solving.
  \item Maintainer of the Online Streams in Mathematics project, which
        provides support for streaming mathematical talks and lectures online
        using free open-source software.
  \item Reviewer for Mathematical Reviews / MathSciNet.
  \item Founder and software engineer for Teloga.com, customer relationship
        management software-as-a-service for collegiate music organizations
        from 2011-2015.
  \item Served the National Youth Leadership Training program at Camp Westmoreland,
        Florence, AL from 2002-2011 as director, quartermaster, and
        numerous other roles.
\end{itemize}

% (e) Collaborators & Other Affiliations: (use the following sections)
% list in alphabetical order, and include current affiliations parenthetically

\section{Collaborators and Other Affiliations}

% Collaborators and Co-editors: past 48 months.  If none, write "none"
\subsection{Collaborators and Co-Editors}
\begin{itemize}
  \item Gary Gruenhage (Auburn University)
  \item Scott Varagona (University of Montevallo)
\end{itemize}
% Graduate Advisors and Postdoctoral sponsors: (your own, no matter how long ago)
\subsection{Graduate Advisors and Postdoctoral Sponsors}
\begin{itemize}
  \item Gary Gruenhage (PhD Advisor, Auburn University)
  \item Alan Dow (Mentor, UNC Charlotte)
\end{itemize}
% Thesis advisor and postgraduate scholar-sponsor:  those you have advised
% in the past 5 years.
% Total number of graduate students advised: X (all time)
% Total number of postdoctoral scholars sponsored: Y (all time)
\subsection{Thesis Advisor and Postgraduate-Scholar Sponsor}
\begin{itemize}
  \item Undergraduate Project: Tanyce James (UNC Charlotte)
\end{itemize}





\newpage

\setcounter{section}{0}
\required{Biographical Sketch: James Dabbs}

% Your Bio should be divided into the following sections
% (a) Professional Preparation (education):
% Undergrad, Major, Year
% Graduate, Major, Year
% Postdoc, Area, Years-Inclusive

\section{Professional Preparation}

\begin{itemize}
  \item University of Georgia \hspace{3em}
        Athens, GA \hspace{3em}
        Mathematics \hspace{3em}
        B.S., 2007
  \item Auburn University \hspace{3em}
        Auburn, AL \hspace{3em}
        Mathematics \hspace{3em}
        M.S., 2011
\end{itemize}


% (b) Appointments:  most recent first.

\section{Appointments}

\begin{itemize}
    \item Lead Instructor, The Iron Yard, 2014-Present
    \item Senior Software Engineer, Emcien, 2012-2014
\end{itemize}

% (c) Publications:  5 related to the proposal, and 5 "Other Significant Publications"

\section{Products}

\subsection{Related to Proposal}

\begin{itemize}
  \item Dabbs, J. (2011).
        \textit{On Manes' countably compact, countably tight, non-compact spaces.}
        Commentationes Mathematicae Universitatis Carolinae, 52(3), 427-433.
  \item Dabbs, J. (2016). pi-base.hs v1.0. Zenodo. 10.5281/zenodo.59230
\end{itemize}

% (d) Synergistic Activities (math-enhancing activities that were not
% part of your main job description, like editorial boards and
% conference organizing - any Math-related volunteer work.
% these are often similar to Broader Impacts

\section{Synergistic Activities}

\begin{itemize}

  \item Lead developer and organizer of Medlink, an open-source project to facilitate distributing medical supplies to Peace Corps volunteers abroad
  \item Responsible for developing curriculum materials on introductory programming and automation at the Iron Yard
  \item Supported Austin Mohr in running undergraduate topology courses at Nebraska Wesleyan University using the PiBase as an educational and exploratory tool
  \item Collaborated with Steven Clontz in building the Teloga.com software platform
\end{itemize}

% (e) Collaborators & Other Affiliations: (use the following sections)
% list in alphabetical order, and include current affiliations parenthetically

\section{Collaborators and Other Affiliations}

% Collaborators and Co-editors: past 48 months.  If none, write "none"
\subsection{Collaborators and Co-Editors}
\begin{itemize}
  \item None in the last 48 months
\end{itemize}
% Graduate Advisors and Postdoctoral sponsors: (your own, no matter how long ago)
\subsection{Graduate Advisors and Postdoctoral Sponsors}
\begin{itemize}
  \item Gary Gruenhage (Graduate Advisor, Auburn University)
\end{itemize}
% Thesis advisor and postgraduate scholar-sponsor:  those you have advised
% in the past 5 years.
% Total number of graduate students advised: X (all time)
% Total number of postdoctoral scholars sponsored: Y (all time)
\subsection{Thesis Advisor and Postgraduate-Scholar Sponsor}
\begin{itemize}
  \item None
\end{itemize}
