%%% Please see https://math.mit.edu/services/grants/index.php for information and instructions
%%%%%%%%% MASTER -- compiles the 4 sections

\documentclass[11pt]{article}


\usepackage[letterpaper, margin=1in]{geometry}



\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\chead{USAFDC GRANT APPLICATION}
\cfoot{Page \thepage}

\parskip0.5em

%PUT YOUR MACROS HERE

\usepackage{amsmath}
\usepackage{amssymb}

\usepackage[hidelinks]{hyperref}

\bibliographystyle{plain}

\begin{document}

% \begin{center}
%   \textbf{
%   UNIVERSITY OF SOUTH ALABAMA FACULTY DEVELOPMENT COUNCIL
%   (USAFDC) PROPOSALS
%   }
% \end{center}
%
% INSTRUCTIONS:  Please refer to the General Guidelines for information on preparing your proposal.
% Submit your completed proposal signed by you, your department chair, and dean to the Graduate School Office, AD 300.
%
%
% \section{PROPOSAL IDENTIFICATION}
%
% \begin{center}
% \begin{tabular}{ccc}
%   & \textbf{NAME} & \textbf{DEPARTMENT} \\
% \textbf{Principal Investigator (PI)} &
% \underline{Steven Clontz} &
% \underline{Mathematics and Statistics}
% \end{tabular}
% \end{center}

% A. Title of Proposal:
%
% \hspace{3em}
% \underline
% {Enhancing Research and Cyberinfrastructure in Set-Theoretic Topology}
%
% B. Project Period:
%
% \hspace{3em}
% FROM: \underline{2017 May 1}
% \hspace{2em}
% TO: \underline{2018 August 31}
%
% C. Amount Requested:
%
% \hspace{3em}
% Total Project Cost:
% \underline{\$0}
%
% \hspace{3em}
% Other Sources:
% \underline{\$0}
%
% \hspace{3em}
% \textbf{Requested from USAFDC:
% \underline{\$0}}
%
%
% \newpage
%
% \section{Principal Investigator (PI):}
%
% Agrees to accept responsibility for the scientific and technical conduct of the proposed project, for provision of the required progress and final reports, and will obtain approval of the appropriate committee, as indicated below, and adhere to applicable regulations for projects involving any of the following:
%
% \begin{center}\footnotesize
% \begin{tabular}{|c|l|c|c|c|}
%   \hline
%   && Needed & Submitted & Approved \\\hline
%   A. & Radiation Safety & N/A && \\\hline
%   B. & Human Subjects & N/A && \\\hline
%   C. & Animal Use & N/A && \\\hline
%   D. & Bio Hazardous Matierals & N/A && \\\hline
%   E. & Export Controls & N/A && \\\hline
%   F. & Other Environmental or Chemical Hazards (Describe Below) & N/A && \\\hline
% \end{tabular}
% \end{center}
%
% Contact Dusty Layton, Director Research Compliance Assurance, CSAB 128, with any questions on items A-F.
%
% Note: I understand that if my proposal is recommended for funding, the award will be conditional until the appropriate approvals above have been received and provided by me to the Graduate School Office.

\setcounter{page}{3}

\centerline{\bf\Large
ABSTRACT
}

\textit{Abstract your proposed project (500-word limit) below using non-technical language easily understandable to persons outside your field.  Remember that a diverse group of faculty will be reviewing your proposal.}\vspace{2em}

The Encyclopedic Database of Topological Spaces, also known as the \(\pi\)-Base and currently hosted at http://topology.jdabbs.com, is an open-source web application with the ability to cross-reference topological spaces, their properties, and the theorems which connect them. As an example, once a user has logged that the closed interval of real numbers between 0 and 1 is ``compact'' and ``Hausdorff'', and EDTS automatically deduces that the space is also ``normal'', and includes this space in search results for normal topological spaces. Historically, researchers memorized hundreds of various spaces, properties, and theorems from papers spread across numerous journal articles, but with our body of knowledge expanding exponentially as time progresses, a robust EDTS would facilitate efficient research by eliminating the difficulty of memorizing or finding such results in the ever-growing and ever-fragmenting literature. For comparison, the similar and more mature On-Line Encyclopedia of Integer Sequences, launched in its current form in late 2010, has been cited in over 5002 works. The applicant will use support from this award to collaborate with fellow researcher Ziqin Feng (Auburn University) and EDTS's main programmer James Dabbs to polish the EDTS prototype for use in production by active researchers in topology. Ultimately, the investigator wishes to establish EDTS as a leading tool in researching and cataloging topological spaces and objects in other mathematical categories; by developing this prototype to a minimally viable product for active use by researchers, the investigator’s competitiveness for external funding to support the project will be increased.

\newpage

\centerline{\bf\Large
DETAILED BUDGET
}

\begin{center}
\begin{tabular}{|l|c|c|c|}
  \hline
  & USAFDC & Other Sources & Total Anticipated Budget \\\hline
  Books &&& \\\hline
  Copying, Printing &&& \\\hline
  Equipment &&& \\\hline
  Postage &&& \\\hline
  Professional Fees** &&& \\\hline
  Software & \$100 && \$100 \\\hline
  \parbox{1.5in}{Student Wages*\\ at \$17.50 per Hr} & \$2100 && \$2100 \\\hline
  Supplies, Consumables &&& \\\hline
  Telephone &&& \\\hline
  Travel & \$2505 && \$2505 \\\hline
  Other &&& \\\hline\hline
  \textbf{TOTAL} & \textbf{\$4705} && \textbf{\$4705} \\\hline
\end{tabular}
\end{center}

* In the budget justification respond to Item 10 of general guidelines.

** Consulting or other professional services that are not available through the University.

\newpage




\centerline{\bf\Large
BUDGET JUSTIFICATION (Required)
}

\textit{Provide a line-by-line justification for each item in the budget, including details of calculated totals as well as how each is necessary for execution of the project.  Itemize equipment and detail travel. For proposals that will take longer than one year to accomplish, the budget and all project plans should fully reflect the timeline required.  Use additional pages as necessary.}\vspace{2em}

\textbf{Software:} \textbf{\$120} is requested to cover hosting costs for the EDTS website on a Digital Ocean cloud server for two years. \textbf{\$80} is requested to obtain the domain name edts.io (or similar) for two years.

\textbf{Student Wages:} One graduate student will be hired for Summer 2018 to assist the investigator with the auditing and expansion of the EDTS database. This student will be compensated at \$17.50 per hour (as limited by the proposal preparation guidelines), 15 hours per week, for 8 weeks, totaling \textbf{\$2100}. The work done by this student supports faculty research by filtering through the trivial (but time-consuming) data entry tasks, freeing the investigator to answer the non-trivial questions associated with this data entry (see Proposed Work Plan for more details).

\textbf{Travel:} The investigator will travel to Auburn, AL for three days during May 2017 and three days during May 2018 to meet with collaborator Prof. Ziqin Feng of Auburn University to develop a plan for auditing the EDTS database for use in cutting-edge research and marketing the tool to the community of researchers, including a selection of appropriate literature to seed the database initially.  Compensation for mileage is estimated at \(\$250\times2=\,\)\textbf{\$500}, and six days of meals is estimated at \textbf{\$330}. (Accommodations will be provided by Dr. Feng.)

The investigator will host the EDTS developer James Dabbs for one week during Summer 2017 to collaborate on the EDTS source code, making the necessary backend and user interface changes to ready it for production on a new domain and server for active use by researchers in topology. Airfare from Washington D.C. to Mobile is estimated at \textbf{\$700}, and five days of meals is estimated at \textbf{\$275}. Hotel accommodations for six nights are estimated at \textbf{\$700}.

\newpage




\centerline{\bf\Large
Proposed Work Plan
}

\textit{Complete the following sections. Adjust the space provided as necessary but the work plan may not exceed five pages, excluding works cited.  Supporting material may be attached as appendices but this is not necessarily encouraged.  Please be reminded that the work plan should be easily understood by a broad academic audience.}


\section*{A. Introduction}

\subsection*{1. State objective(s) of proposed work.}

The main objective of this project is to mature the \(\pi\)-Base web application
for cataloging topological spaces, theorems, and properites from a casual
side-project into a robust research tool for mathematicians in the fields of
general and set-theoretic topology, an Encylopedic Database of Topological
Spaces (EDTS). The current application, hosted at
http://topology.jdabbs.com/, is generally recieved well as a novelty by
researchers, but has several flaws preventing it from being used as a
reference in serious research.

The most glaring of these is a lack of
peer-review; the \(\pi\)-Base database is currently populated by a mix of
results from
the literature and unverified data from unvetted users. This will be
corrected by auditing the contents of the database to reference peer-reviewed
sources where possible, and flagging other entries as unverified.
In addition, several important data points from the literature are not
represented in the database, leaving too many holes for it to serve as
an efficient resource resource for most researchers.
To that end, the database will be expanded to a critical mass that meets the
needs of several specific researchers in several niches of set-theoretic
topology, who will be recruited by the investigator and his colleague Prof.
Ziqin Feng of Auburn University. To support these necessary enhancements,
the investigator will collaborate with \(\pi\)-Base developer James Dabbs to
write the code required for these new features and user interface improvements.

In addition to revolutionizing the way research in set-theoretic and general
topology is done, an additional objective of the project is to develop
a mechanism for finding suitable undergraduate research projects in those
fields. Research in mathematics typically involves finding logical proofs or
counter-examples to mathematical conjectures which have yet to be solved. Due
to this, it is often difficult to find
accessible problems for undergraduates which would constitute
truly original research. Most problems on the mind of topological researchers
that could be tackled by undergraduates
are usually solved trivially or at least in short time by mathematicians with
more experience. However, once the EDTS database reflects the cutting-edge
of topological research, it will be able to
automatically produce open questions that are
truly unknown, yet have not been considered by PhD researchers. Of course,
what makes a question in topology ``interesting'' to researchers is determined
by humans working in the field, so the majority of these
computer-generated open questions
would not be attractive to more advanced researchers, even those that are
easily seen to not be difficult to solve. Such questions
would be perfect for
creating undergraduate projects or theses that allow students to work on
truly original research in a field traditionally inaccessible to students
without graduate coursework in the area.







\subsection*{2. Background:  Review scholarly work in the area and its relationship to the proposed study.}

In 1970, Steen and Seebach published a handbook
covering \(143\) important examples of topological spaces, entitled
\textit{Counterexamples in Topology} \cite{MR1382863}. Renowned researcher
Mary Ellen Rudin wrote the following in her review \cite{MR1536430}
of the original text.
``\textit{Counterexamples in Topology} is a valuable addition to the small
collection of books I keep on the shelf in my office.'' ``The book is
completely unique; no other book now in print serves its purpose.''
Recognizing the maze of counterexamples littered throughout the
field of set-theoretic topology, Rudin suggested that not only students could
benefit from the text as a guidebook, but
``Even those of us who work exactly in the area will profit from
its organization.''

Several other \textit{Counterexamples} texts
in the tradition of Stein and Seebach have been published in several fields,
including (but not limited to) real analysis \cite{MR1256489}, differential
equations \cite{MR1113487}, probability \cite{MR930671}, and
graph theory \cite{MR0491272}.
The utility of such books is evident to the working mathematician, as it is
invaluable to have a convenient resource that efficently
answers questions of the following forms:
\begin{itemize}
  \item ``Does the object \(T\) have property \(X\)?''
  \item ``Do all objects with properties \(\{A,B,C\}\) also have properties
          \(\{X,Y,Z\}\)?''
  \item ``Do we already know of an object that satisifes properties
          \(\{A,B,C\}\)?''
\end{itemize}

The limitations of these publications are just as evident. When entered into
the existing \(\pi\)-Base prototype and automatically checked by the computer,
several non-obvious errors were unearthed in
\textit{Counterexamples in Topology}. This is to be
expected in such an ambitious work, but certainly would be a frustrating
discovery for a mathematican relying on the faulty data. A computer-verified
resource such as EDTS would prevent such inconsistencies from ever appearing
in the database.

Furthermore, over \(45\) years later, \textit{Counterexamples in Topology}
is no longer on the cutting edge of research. It was originally written with
the assistance of an NSF-funded undergraduate research experience, and
represented the most recent developments of the time. However, as a book,
it is not a living document and cannot evolve with the active community of
research to continually serve its needs. The EDTS will continually be updated
and expanded, allowing it to serve researchers of topology for years to come.
In addition, the software that will power EDTS will be written in a generic
fashion, so that it may similarly be used to power databases for literally
any category of mathematics, including those with existing books and databases
of counterexamples, and those which as of yet do not.

The benefits of such a robust database are already known in another field of
mathematics. The On-Line Encyclopedia of Integer Sequences, hosted at
https://oeis.org, is a frequently used and cited resource in number theory
and its related fields.
Since the site launched in its current form in late 2010, the OEIS
has been cited in over 5002 works \cite{OEIScitations}. The success of OEIS
is due to its ease of access and use by both researchers and students of
mathematics, its robust referencing system connecting the database to the
literature, and the community that maintains it. It is the investigator's
expectation that an enhanced Encylopedic Database of Topological Spaces can
acheive a similar level of success and notability by following the example
of OEIS.







\subsection*{3. Preliminary work:  Describe any work you have begun that relates to the project and how the proposed work validates or extends that work.}

The \(\pi\)-Base protoype currently hosted at http://topology.jdabbs.org
represents the preliminary work done for this project by the investigator,
its developer, and the small community that has contributed to it
over the past few years of its existence (similar to Wikipedia, but without
the sizable userbase of content experts). Specifically, the investigator
has contributed to the project by entering data related to his own research
in set theoretic topology, for example
\cite{MR3467819,MR3482726,MR3227201,MR3438747}. Using this prototype has
allowed the investigator to cleanly catalog the raw data associated with
the results of his research and generate open questions that have yet to be
solved by those results; for example, despite the theorem
http://topology.jdabbs.com/theorems/168
(discussed in \cite{clontzMengerGamePreprint}) which states that all
\(2\)-Markov-Winning Menger spaces are Winning Menger, there is no known
counter-example to the converse: a Winning Menger space which isn't also
\(2\)-Markov-Winning Menger.

Despite its promise, the utility of the existing prototype is limited by the
current functionality of the site and the limited involvement by the broader
community of researchers. The proposed work will allow the prototype to
mature into a robust web applicaiton that immediately communicates its
utility to acitve researchers. Combined with the proposed improvments to the
\(\pi\)-Base software and user interface, the recruitment of leading
researchers to contribute and maintain the database by the investigator and
Dr. Feng will establish the new EDTS application as a primary resource for
researchers to find and cite research results in topology. After its
success is established, the EDTS software can then be expanded to serve other
fields of mathematical research as well.











\subsection*{4. Significance:  State the potential importance of the proposed work to the field of study.  Also, please attach a letter of support from your department chair (or equivalent position) evaluating the merit of the proposal.}

asdf













\section*{B. Methodology}

\subsection*{1.	Describe in detail your proposed work or approach to accomplishing the objective(s).}















\subsection*{2. If data are to be collected, outline the means by which they will be analyzed.}
















\subsection*{3. Timeline.  Indicate the proposed timeline for project completion. For projects exceeding one year (12 calendar months), provide justification.}














\section*{C. Anticipated outcomes:}

\subsection*{1. Include names of probable journals, publishers, etc.  A final written report and a presentation of project results at the Annual Research Forum are required; failure to comply may jeopardize future USAFDC funding opportunities.}











\subsection*{2.	Describe plans for extending the project via external support, if any. (The USA Office of Research can provide help in identifying possible sources of external support relative to this proposal.)}
















\section*{D.	Facilities and Other Resources:}

\textit{List the facilities available for this project, departmental contributions, and other support for the project not listed in the budget and budget justification pages.}




















\section*{E.	List outcomes and dates of USAFDC grants received in past five years.}

\textit{Provide titles and dates.  List date and title of USAFDC Spring Forum poster presentation.}















\section*{F.	Describe how the proposed project differs from any previous USAFDC-funded project.}

















\section*{G. List of references cited in the grant application.}

\bibliography{../bib}



% BIOGRAPHICAL SKETCH
% Do not attach a resume. Use the guidelines at:  http://www.southalabama.edu/departments/eforms/graduateschool/biosketch.docx



\end{document}
